Customize Your Threshold

### 2021-09-29 app/app.Rmd

```{r data}
wages_hs <- readRDS(here::here("app/wages_hs.rds")) %>%
    dplyr::select(-`X1.x`, -`X1.y`)
```

@@

```{r}
sliderInput("th", "Threshold:",
            min = 0.01,
            max = 1,
            value = 5)
```

@@

Row {data-height=400}
-------------------------------------

@@

@@

```{r}
p(icon("info-circle", lib = "font-awesome"), "Summary statistics of wages in imputed data")
renderText({paste0("Minimum = ", round(min(pred()$wages_rlm), 2), " (Original = 0.01)")})
renderText({paste0("Median = ", round(median(pred()$wages_rlm), 2), " (Original = 7.2)")})
renderText({paste0("Mean = ", round(mean(pred()$wages_rlm), 2), " (Original = 11.87)")})
renderText({paste0("Maximum = ", round(max(pred()$wages_rlm), 2), " (Original = 33400)")})
```

>>>>

```{r data}
wages_hs <- readRDS(here::here("wages_hs.rds")) %>%
    dplyr::select(-`X1.x`, -`X1.y`)
```

@@

```{r}
sliderInput("th", "Slide to set the threshold",
            min = 0.01,
            max = 1,
            value = 5)
```

@@

```{r}
p(icon("info-circle", lib = "font-awesome"), strong("More"))
```

Have any issue or question? 
Please put it [here](https://github.com/numbats/yowie/issues)

Row {data-height=300}
-------------------------------------

@@

```{r}
p(icon("info-circle", lib = "font-awesome"), "The imputed plot shows how the data changes after the threshold is customized. You can then compare it with the original plot. The following is the summary statistics of the imputed data.")
```

@@

```{r}
renderText({paste0("Minimum = ", round(min(pred()$wages_rlm), 2), " (Original = 0.01)")})
renderText({paste0("Median = ", round(median(pred()$wages_rlm), 2), " (Original = 7.2)")})
renderText({paste0("Mean = ", round(mean(pred()$wages_rlm), 2), " (Original = 11.87)")})
renderText({paste0("Maximum = ", round(max(pred()$wages_rlm), 2), " (Original = 33400)")})
```
